---
title: "EuroSpA CC Data Screening, script last updated 22 March 2022"
author: ""
co- author: "Alexander Kruhøffer Bloch Andersen"
date: ""
output: html_document
---

## 1. Instructions

To run this Rmd file in RStudio:

 - Ensure data files and calculator_basdai.R are placed in the same folder as this Rmd file
 - Hash out all filenames except one to ensure the desired data file is used
 - Use "Knit to HTML" to produce html file
 - Rename the html file by appending

```{r, eval=TRUE, echo=F, fig.height = 10, fig.width = 10}
if(Sys.info()[7] == "AAND0774"){
  setwd("C:/Users/AAND0774/Documents/GitHub/eurospa.data_pooling_studya2a3/screening/")
}else{
  if(Sys.info()[7] == "simras"){
  setwd("C:/Users/simras/Documents/GitHub/eurospa.data_pooling_studya2a3/screening/")
  }else{
      setwd("C:/Users/AAND0774/Documents/GitHub/eurospa.data_pooling_studya2a3/screening/")
  }
}

#import data using readxl package
library(readxl) #read_excel
library(writexl) #write_xlsx
library(parsedate)
library(formattable)
#hash out all filenames except one to ensure the desired data file is used

#handling of dates
cast_dates = function(data){
  date_variables = c("bio_drug_start_date","bio_drug_stop_date","date_of_last_visit","date_of_first_visit","end_of_follow_up_date","data_cut_date")
  
  for (var in date_variables){
    if(!is.null(eval(parse(text=paste("data","$",var,sep=""))))){
      data[,var] = parse_date(data[,var])
    }
  }
  return(data)
}


#filename <- "../datasets/CZ/data_cz_20220315_v5.txt"
#metadata = "../datasets/CZ/metadata_cz_20220223_v2.xlsx"

#filename <- "../datasets/CZ/data_cz_20220315_v5.txt"
#metadata = "../datasets/CZ/metadata_cz_20220223_v2.xlsx"

#filename <- "../datasets/FI/study_A2_A3_Finland_6.4_version_8.0.txt"
#metadata = "../datasets/FI/metadata_master_raw_study_A2_A3 _Finland_28.3_version_5.0_SHR.xlsx"


#filename <- "../datasets/PT/data_PT_20220212_v7.txt"
#metadata = "../datasets/PT/metadata_PT_20220212_v3.xlsx"

#filename <- "../datasets/SI/data_si_20220217_v8.txt"
#metadata = "../datasets/SI/metadata_SI_study_A2_A3_20220217_version_2.2.xlsx"

#filename <- "../datasets/CH/data_switzerland_20220201_1.txt"
#metadata = "../datasets/CH/metadata_switzerland_20220201_1.xlsx"

#filename <- "../datasets/NO/data_NORWAY_20220423_7.txt"
#metadata = "../datasets/NO/metadata_master_raw_study_A2_A3 version_NORWAY.xlsx"

#filename <- "../datasets/SE/data_Sweden_11052021_v1.txt"
#metadata = "../datasets/SE/metadata_Sweden_18032021_v2.xlsx"

#filename = paste("../datasets/UK/data_UK_140422_v6.txt",sep="")
#metadata = paste("../datasets/UK/metadata_UK_140422_version_4.0.xlsx",sep="")

#filename = paste("../datasets/","ES/biobad_eurospa_apr29v5.txt",sep="")
#metadata <- paste("../datasets/","metadata_ES_study_A2_A3_v1_20220419.xlsx",sep="")

filename = paste("../datasets/","ET/Estonia_22.03.1.txt",sep="")
metadata <- paste("../datasets/","ET/metadata_master_raw_study_A2_A3 version_2.xlsx",sep="")

#filename = paste("../datasets/","SF/study_A2_A3_Finland_28.4_version_9.0.txt",sep="")
#metadata <- paste("../datasets/","SF/metadata_master_raw_study_A2_A3 _Finland_28.4_version_6.0.xlsx",sep="")

#filename <- "../datasets/PT/metadata_PT_20210314_v3.txt"
#metadata = "../datasets/PT/20210302_metadata_master_raw_studyA1.xlsx"

#filename <- "../datasets/RO/data_romania_20220313_v2.txt"
#metadata = "../datasets/RO/metadata_romania_20220113_v3.xlsx"

#filename <- "../datasets/IS/bdmards_dt_merge_washed_IS_20220502.csv"
#metadata = "../datasets/IS/metadata_master_is_raw_study_A2_A3_v1_0.xlsx"

#filename <- "../datasets/DK/bdmards_dt_merge_washed_DK_20220502.csv"
#metadata = "../datasets/DK/metadata_master_dk_raw_study_A2_A3_v1_0.xlsx"

#filename <- "../datasets/IT/data_italy_20220409_3.txt"
#metadata = "../datasets/IT/metadata_master_raw_study_A2_A3 version_1.0_Italy_20220408_v1.0.xlsx"

#filename <- "../datasets/NO/data_NORWAY_20220425_10.txt"
#metadata = "../datasets/NO/metadata_master_raw_study_A2_A3 version_NORWAY.xlsx"

#filename = paste("../datasets/","ES/data_ES_20210905.txt",sep="")
#metadata <- paste("../datasets/","ES/metadata_ES_studyA1_v2.xlsx",sep="")

#filename = paste("../datasets/","NL/data_NL_06052021_v2.1.txt",sep="")
#metadata = paste("../datasets/","NL/metadata_NL_22032021_studyA1_v1.5.xlsx",sep="")

#filename <- "../datasets/TR//bdmards_dt_merge_washed_TR_20210724.csv"
#metadata = "../datasets/TR/metadata_TR_20210224_v4nsk.xlsx"

#filename <- "../datasets/IT/20210923_data_ver9.txt"
#metadata = "../datasets/IT/20210302_metadata_master_raw_studyA1_20210524.xlsx"

#filename <- "../datasets/IS/bdmards_dt_merge_washed_IS_20210724.csv"
#metadata = "../datasets/IS/metadata_IS_20210224_v4nsk.xlsx"

#filename <- "../datasets/DK/bdmards_dt_merge_washed_DK_20220127.txt"

#filename <- "../datasets/SI/data_si_20220217_v4.txt"


#md <- read_excel(metadata)

d <- read.table(filename,header=T,sep = "\t")                                               # data reading plan A
#d <- as.data.frame(read.csv(filename,sep = "\t",header=TRUE,na.strings=c("NA","NaN", ""))) # data reading plan B


d = cast_dates(d)
#print(head(d))
#print to html

print(paste("File name:       ", filename))
print(paste("System time:     ", Sys.time()))
print(paste("Country:         ", unique(d$country)))


#handling of basdai

#this is a practical way for scaling range to be 0 to 10, in case it is supplied as 0 to 100, based on observed max value
#a more robust solution might be to import metadata and use range as specified in metadata

#if("basdai_1_fatigue" %in% colnames(d)){
#  if(max(d$basdai_1_fatigue, na.rm = TRUE) > 10) {d$basdai_1_fatigue <- d$basdai_1_fatigue/10}
#}

#if("basdai_2_pain_spinal" %in% colnames(d)){
#if(max(d$basdai_2_pain_spinal, na.rm = TRUE) > 10) {d$basdai_2_pain_spinal <- d$basdai_2_pain_spinal/10}
#}

#if("basdai_3_pain_joints" %in% colnames(d)){
#if(max(d$basdai_3_pain_joints, na.rm = TRUE) > 10) {d$basdai_3_pain_joints <- d$basdai_3_pain_joints/10}
#}

#if("basdai_4_tender" %in% colnames(d)){
#if(max(d$basdai_4_tender, na.rm = TRUE) > 10) {d$basdai_4_tender <- d$basdai_4_tender/10}
#}

#if("basdai_5_stiffness_severity" %in% colnames(d)){
#if(max(d$basdai_5_stiffness_severity, na.rm = TRUE) > 10) {d$basdai_5_stiffness_severity <- d$basdai_5_stiffness_severity/10}
#}

#if("basdai_6_stiffness_duration" %in% colnames(d)){
#if(max(d$basdai_6_stiffness_duration, na.rm = TRUE) > 10) {d$basdai_6_stiffness_duration <- d$basdai_6_stiffness_duration/10}
#}

if("basdai" %in% colnames(d)){
  if(max(d$basdai, na.rm = TRUE) > 10) {
    d$basdai <- d$basdai/10
  }
}

#calculate basdai_out

#source("calculator_basdai.R")

#d$basdai_out <- NA

#if(all(c("basdai_1_fatigue", "basdai_2_pain_spinal", "basdai_3_pain_joints",
#         "basdai_4_tender", "basdai_5_stiffness_severity", "basdai_6_stiffness_duration") %in% colnames(d))){
#  d$basdai_out <- calculator_basdai(
#  d$basdai_1_fatigue,
#  d$basdai_2_pain_spinal,
#  d$basdai_3_pain_joints,
#  d$basdai_4_tender,
#  d$basdai_5_stiffness_severity,
#  d$basdai_6_stiffness_duration)
#}

#check for basdai inconsistencies

#if("basdai" %in% colnames(d) & !all(is.na(d$basdai_out))){
#  plot(d$basdai, d$basdai_out, main = "Check for inconsistencies between basdai items and basdai")
#  abline(b = 1, lty = 2)

#basdai_inconsistencies <- (d[round(d$basdai, 1) != round(d$basdai_out, 1) & !is.na(d$basdai) & !is.na(d$basdai_out),
#        c("row_id", "basdai_1_fatigue", "basdai_2_pain_spinal", "basdai_3_pain_joints",
#          "basdai_4_tender", "basdai_5_stiffness_severity", "basdai_6_stiffness_duration", "basdai_out", "basdai")])
#colnames(basdai_inconsistencies)[2:7] <- c("item1", "item2", "item3", "item4", "item5", "item6")
#options(tibble.print_max = Inf)
#basdai_inconsistencies$diff <- round(abs(basdai_inconsistencies$basdai_out - basdai_inconsistencies$basdai),2)
#basdai_inconsistencies <- basdai_inconsistencies[order(basdai_inconsistencies$diff, decreasing = TRUE),]
#basdai_inconsistencies

#}

#use basdai_out to overwrite any existing basdai values where basdai_out has a value different from NA
#this is a practical fix for handling the situation where some rows may have "basdai" but not individual items,
#while other rows may have individual items (these rows may or may not also have "basdai")

#if(!("basdai" %in% colnames(d))) {
#  d$basdai <- NA
#}

#if("basdai_out" %in% colnames(d)){
#  d$basdai[!is.na(d$basdai_out)] <- d$basdai_out[!is.na(d$basdai_out)]
#}
  
#ensure weeks_delta_to_baseline is numeric to allow plotting
# overwite patient IDs
old_pids = d$patient_id
num_patients = length(unique(d$patient_id))
new_patient_ids = sample(x=1:num_patients,size=num_patients)
i = 1
for(pid in unique(old_pids)){
  d$patient_id[old_pids == pid] <- new_patient_ids[i]
  i = i + 1
}

d$weeks_delta_to_baseline <- as.numeric(d$weeks_delta_to_baseline)
d<-d[d$weeks_delta_to_baseline>-15,]
```

## 2. Descriptives

```{r, eval=TRUE, echo=TRUE}

Hmisc::describe(d)

```

## 3. bio_drug_start_date for patients with only one row of data

```{r, eval=TRUE, echo=TRUE}

unique_ids <- unique(d$patient_id)
nrows_per_unique_ids <- rep(NA, length(unique_ids))
for(i in 1:length(unique_ids)){
  sub <- d[d$patient_id == unique_ids[i],]
  nrows_per_unique_ids[i] <- nrow(sub)
}
one_row_patients <- unique_ids[nrows_per_unique_ids == 1]
sort(d$bio_drug_start_date[d$patient_id %in% one_row_patients])

```

## 4.Variable constistency between xray-sacroiliitis and hla_b27 variables
```{r,eval=TRUE,echo=TRUE}
if(!is.null(d$new_york_criteria_4ab_xray_sacroiliitis) && !is.null(d$asas_criteria_13_xray_sacroiliitis)){
gmodels::CrossTable(d$new_york_criteria_4ab_xray_sacroiliitis,d$asas_criteria_13_xray_sacroiliitis,missing.include=FALSE,prop.c=FALSE,prop.r=FALSE,prop.chisq=FALSE,format="SPSS",dnn=c("New York Criteria 4ab: X-ray sacroiliitis","ASAS Criteria 13: X-ray sacroiliitis"),percent = (format == "SPSS"))
}else {if(is.null(d$new_york_criteria_4ab_xray_sacroiliitis)){print("New York Criteria 4ab not provided")}
      if(is.null(d$asas_criteria_13_xray_sacroiliitis)){print("ASAS Criteria 13 not provided")}
    }

if(!is.null(d$hla_b27) && !is.null(d$asas_criteria_10_hla_b27)){
gmodels::CrossTable(d$hla_b27,d$asas_criteria_10_hla_b27,missing.include=FALSE,prop.c=FALSE,prop.r=FALSE,prop.chisq=FALSE,format="SPSS",dnn=c("hla_b27","ASAS Criteria 10: hla_b27"),percent = (format == "SPSS"))
}else{if(is.null(d$hla_b27)){print("hla_b27 not provided")}
      if(is.null(d$asas_criteria_10_hla_b27)){print("ASAS Criteria 10 not provided")}
    }


```

## 5. Number of rows per patient and treatment series

```{r, eval=TRUE, echo=TRUE}

#table of rows per patient, all treatment series

table(table(d$patient_id))

#table of rows per patient, restricted to 1st treatment series

table(table(d$patient_id[d$bio_drug_series_number == 1]))

#table of rows per patient, restricted to 2nd treatment series

table(table(d$patient_id[d$bio_drug_series_number == 2]))

#table of rows per patient, restricted to 3rd treatment series

table(table(d$patient_id[d$bio_drug_series_number == 3]))

#table of rows per patient, restricted to 4th treatment series

table(table(d$patient_id[d$bio_drug_series_number == 4]))

#table of rows per patient, restricted to 5th treatment series

table(table(d$patient_id[d$bio_drug_series_number == 5]))

```

## 6. Longitudinal plots of visits for 1st, 2nd and 3rd treatment series, sample of up to 100 patients

```{r, eval=TRUE, echo=TRUE, fig.height = 15, fig.width = 6}

for(i in 1:3){
  set.seed(123)
  unique_ids <- unique(d$patient_id[d$bio_drug_series_number == i & as.Date(d$bio_drug_start_date) > as.Date("2014-12-31")])
  n <- min(100, length(unique_ids))
  sample_patient_ids <- sample(unique_ids, n) #sample up to 100 patients (if less than 100 patients are available, choose all)
  d_sub <- d[d$bio_drug_series_number == i & d$patient_id %in% sample_patient_ids,]
  stripchart(d_sub$weeks_delta_to_baseline ~ d_sub$patient_id,
           axes = FALSE, main = paste0("BIO DRUG SERIES ", i, ", WEEKS DELTA TO BASELINE\nSAMPLE OF UP TO 100 PATIENTS"))
  
  ### adds red points to mark bio_drug_stop_date in comparison to weeks_delta_to_baseline
  d_sub$bio_drug_weeks_delta_to_baseline=difftime(strptime(d_sub$bio_drug_stop_date,format="%Y%m%d"),
                                                  strptime(d_sub$bio_drug_start_date,format="%Y%m%d"),units="weeks")
  if(is.na(unique(d_sub$bio_drug_weeks_delta_to_baseline))){
    d_sub$bio_drug_weeks_delta_to_baseline=difftime(as.Date(d_sub$bio_drug_stop_date),
                                                    as.Date(d_sub$bio_drug_start_date),units="weeks")}
  d_sub$bio_drug_weeks_delta_to_baseline[is.na(d_sub$bio_drug_weeks_delta_to_baseline)] = Inf
  stripchart(d_sub$bio_drug_weeks_delta_to_baseline ~ d_sub$patient_id, col="red", add=TRUE,  pch=19)
  
  ## make a list of ID with bio_drug_series_numbers equal from i to make points for end_of_follow_up_date and date_of_last_visit
  keep_id<-c()
  for(pid in unique_ids){
    if(length(unique(d$bio_drug_series_number[d$patient_id==pid]))==i){
      keep_id<-c(keep_id,pid)
    }
  }
  
  ### adds blue crosses to mark end_of_follow_up_date in comparison to weeks_delta_to_baseline
  if("end_of_follow_up_date" %in% colnames(d_sub)){
    d_sub$ending_follow_up_weeks_delta_to_baseline=difftime(as.Date(d_sub$end_of_follow_up_date),as.Date(d_sub$bio_drug_start_date),units="weeks")
  
  
  d_sub$ending_follow_up_weeks_delta_to_baseline[is.na(d_sub$ending_follow_up_weeks_delta_to_baseline) | 
                                                   !(d_sub$patient_id %in% keep_id)] = Inf
  stripchart(d_sub$ending_follow_up_weeks_delta_to_baseline ~ d_sub$patient_id, col="blue", add=TRUE,  pch=4, lwd=2)
  }
  ### adds green triangles to mark date_of_last_visit in comparison to weeks_delta_to_baseline
  if("date_of_last_visit" %in% colnames(d_sub)){
    d_sub$last_visit_weeks_delta_to_baseline=difftime(as.Date(d_sub$date_of_last_visit),as.Date(d_sub$bio_drug_start_date),units="weeks")
  
  
  d_sub$last_visit_weeks_delta_to_baseline[is.na(d_sub$last_visit_weeks_delta_to_baseline) | 
                                                   !(d_sub$patient_id %in% keep_id)] = Inf
  stripchart(d_sub$last_visit_weeks_delta_to_baseline ~ d_sub$patient_id, col="green", add=TRUE,  pch=2, lwd=2)
  }
  axis(1, at = c(0, 26, 52, 104))
  abline(v = 0, lty = 2, col = "red")
  abline(h = 1:n)
  
  ### variable description
  points(10,0,pch=0,col="black")
  text(25,0,label=":visit")
  points(90,0,pch=19,col="red")
  text(115,0,label=":End of current treatment")
  if("end_of_follow_up_date" %in% colnames(d_sub)){
  points(10,-2,pch=4,lwd=2,col="blue")
  text(25,-2,label=":Final end of Follow up")}
  if("date_of_last_visit" %in% colnames(d_sub)){
  points(90,-2,pch=2,lwd=2,col="green")
  text(115,-2,label=":last visit")}
}

```

## 7. Longitudinal plot of C-reactive protein (CRP) for 1st treatment series, sample up to 500 patients

```{r, eval=TRUE, echo=TRUE, fig.height = 15, fig.width = 15}

if("crp" %in% colnames(d)){

#for bio drug series number 1, sample up to 500 patient ids, plot crp longitudinally

unique_ids <- unique(d$patient_id[d$bio_drug_series_number == 1])
n <- min(500, length(unique_ids))
sample_patient_ids <- sample(unique_ids, n) #sample up to 500 patients (if less than 500 are available, choose all)
d_sub <- d[d$bio_drug_series_number == 1 & d$patient_id %in% sample_patient_ids,]
d_sub <- d_sub[order(d_sub$weeks_delta_to_baseline),]
d_sub <- d_sub[order(d_sub$patient_id),]
plot(0, type = "n", axes = FALSE, xlim = c(-15, 130), ylim = c(0, 100),
     xlab = "weeks_delta_to_baseline", ylab = "crp")
for(i in 1:length(sample_patient_ids)){
  lines(d_sub$crp[d_sub$patient_id == sample_patient_ids[i]] ~
          d_sub$weeks_delta_to_baseline[d_sub$patient_id == sample_patient_ids[i]],
        col = scales::alpha("blue", 0.1), lwd = 5)
}
axis(1, at = c(0, 26, 52, 104))
axis(2, at = c(0, 25, 50, 75, 100))
abline(v = 0, lty = 2, col = "red")

}

```


## 8. Longitudinal plot of BASDAI for 1st treatment series, sample up to 500 patients

```{r, eval=TRUE, echo=TRUE, fig.height = 15, fig.width = 15}

if("basdai" %in% colnames(d)){

unique_ids <- unique(d$patient_id[d$bio_drug_series_number == 1])
n <- min(500, length(unique_ids))
sample_patient_ids <- sample(unique_ids, n) #sample up to 500 patients (if less than 500 are available, choose all)
d_sub <- d[d$bio_drug_series_number == 1 & d$patient_id %in% sample_patient_ids,]
d_sub <- d_sub[order(d_sub$weeks_delta_to_baseline),]
d_sub <- d_sub[order(d_sub$patient_id),]
plot(0, type = "n", axes = FALSE, xlim = c(-15, 130), ylim = c(0, 10),
     xlab = "weeks_delta_to_baseline", ylab = "basdai")
for(i in 1:length(sample_patient_ids)){
  lines(d_sub$basdai[d_sub$patient_id == sample_patient_ids[i]] ~
          d_sub$weeks_delta_to_baseline[d_sub$patient_id == sample_patient_ids[i]],
        col = scales::alpha("blue", 0.1), lwd = 5)
}
axis(1, at = c(0, 26, 52, 104))
axis(2, at = c(0, 5, 10))
abline(v = 0, lty = 2, col = "red")

}

```


## 9. Longitudinal plot of tender_joints_28 for 1st treatment series, sample up to 500 patients

```{r, eval=TRUE, echo=TRUE, fig.height = 15, fig.width = 15}

if("tender_joints_28" %in% colnames(d)){
  
unique_ids <- unique(d$patient_id[d$bio_drug_series_number == 1])
n <- min(500, length(unique_ids))
sample_patient_ids <- sample(unique_ids, n) #sample up to 500 patients (if less than 500 are available, choose all)
d_sub <- d[d$bio_drug_series_number == 1 & d$patient_id %in% sample_patient_ids,]
d_sub <- d_sub[order(d_sub$weeks_delta_to_baseline),]
d_sub <- d_sub[order(d_sub$patient_id),]
plot(0, type = "n", axes = FALSE, xlim = c(-15, 130), ylim = c(0, 28),
     xlab = "weeks_delta_to_baseline", ylab = "tender_joints_28")
for(i in 1:length(sample_patient_ids)){
  lines(d_sub$tender_joints_28[d_sub$patient_id == sample_patient_ids[i]] ~
          d_sub$weeks_delta_to_baseline[d_sub$patient_id == sample_patient_ids[i]],
        col = scales::alpha("blue", 0.1), lwd = 5)
}
axis(1, at = c(0, 26, 52, 104))
axis(2, at = c(0, 5, 10, 28))
abline(v = 0, lty = 2, col = "red")

}

```




## 10. Precision of bDMARDs dosis and application interval 
```{r, eval=TRUE, echo=FALSE, fig.height = 15, fig.width = 15}
# extract the unique bio drug names for which drug standards have been given
drug_names=c("abatacept","adalimumab","apremilast","baricitinib","certolizumab","etanercept","golimumab","guselkumab","infliximab","ixekizumab","rituximab","secukinumab","tocilizumab","tofacitinib","upadacitinib","ustekinumab")

final_names=c()

dosematch=c()
intervalmatch=c()

dosevariansmatch=c()
intervalvariansmatch=c()

# looping over data to check bio_drug_dosing_interval and bio_drug_dose
for(name in drug_names){
  #create subset of data from drugnames
  sub<-d[d$bio_drug_name == name,]
  dose_issue <- 0
  dose_varians_issue <- 0
  
  interval_issue <- 0
  interval_varians_issue <- 0
  
  #loop across subset
  for(i in 1:nrow(sub)){
    
    #select standard to be used based on diagnosis group
    if(is.na(sub[i,"diagnosis_group"])){
      #print(paste0("patient ",sub[i,"patient_id"]," have not been diagnosed with neither AxSpA nor SpA"))
      if(is.na(sub[i,"patient_id"])){
        break
      }
      # skip iteration, if no diagnosis group have been given
      next 
    }else{
      diagnosis <- sub[i,"diagnosis_group"]
    }
    
    amount=as.numeric(sub[i,"bio_drug_dose"])
    treat=sub[i,"bio_drug_dosing_interval"]
    
    if(name=="abatacept"){
      if(diagnosis=="psa"){
        if(!(is.na(sub[i,"weight"]))){
          if(!(is.na(sub[i,"weight"])) && as.integer(sub[i,"weight"])<60){
            dose=c(125,500)
          }else if(!(is.na(sub[i,"weight"])) && as.integer(sub[i,"weight"])>=60 | as.integer(sub[i,"weight"])<=100){
            dose=c(125,750)
          }else if(!(is.na(sub[i,"weight"])) && as.integer(sub[i,"weight"])>100){
            dose=c(125,1000)
          }
        }else{
          dose=c(125,500,750,1000)
        }  
        interval=c(1,14,28)
      }
    }else if(name=="adalimumab"){
     dose=40
     interval=14 
    }else if(name=="apremilast"){
      if(diagnosis=="psa"){
        if(sub[i,"weeks_delta_to_baseline"]==0){
          dose=c(10,20,30,40,50,60)
          interval=c(1,2,3,4,5,6)
        }else{
          dose=c(30,60)
          interval=1
        }
      }else{
        dose_issue=dose_issue+1
        interval_issue=interval_issue+1
        next
      }
    }else if(name=="baricitinib"){
      dose=c(2,4)
      interval=1
    }else if(name=="certolizumab"){
      if(diagnosis=="spa"){
        if(sub[i,"weeks_delta_to_baseline"]==0){
          dose=400
          interval=c(1,14,28)
        }else if(sub[i,"weeks_delta_to_baseline"]>=2){
          dose=200
          interval=14
        }else if(sub[i,"weeks_delta_to_baseline"]>=4){
          dose=400
          interval=28
        }
      }else if(diagnosis=="psa"){
        if(sub[i,"weeks_delta_to_baseline"]==0){
          dose=400
          interval=c(1,14,28)
        }else{
          dose=200
          interval=14
        }
      }
    }else if(name=="etanercept"){
      dose=c(25,50)
      interval=c(2,3,7)
    }else if(name=="golimumab"){
      if(!is.na(sub[i,"weight"]) && sub[i,"weight"]>100){
        dose=100
      }else{
        dose=50
      }
      interval=28
    }else if(name=="guselkumab"){
      if(diagnosis=="psa"){
        dose=100
        if(sub[i,"weeks_delta_to_baseline"]==0){
          interval=c(1,28)
        }else{
          interval=c(28,56)
        }
      }else{
        dose_issue=dose_issue+1
        interval_issue=interval_issue+1
        next
      }
    }else if(name == "infliximab"){
      if(!is.na(sub[i,"bio_drug_dose"]) && !is.na(sub[i,"weight"])){
        dose=5 
        }
        if(diagnosis=="psa"){
          interval=c(1,14,42)
        }else if(diagnosis=="spa" || diagnosis=="axspa"){
          interval=c(1,14,42,56)
        }
    }else if(name=="ixekizumab"){
      if(diagnosis=="psa"){
        if(sub[i,"weeks_delta_to_baseline"]==0){
          dose=160
          interval=1
        }else{
          dose=80
          interval=c(14,28,42,56,70,84)
        }
      }else{
        dose_issue=dose_issue+1
        interval_issue=interval_issue+1
        next
      }
    }else if(name=="rituximab"){
      if(sub[i,"weeks_delta_to_baseline"]==0){
        dose=seq(500,1000)
        interval=c(1,15)
      }else{
        dose=1000
        interval=seq(182,365)
      }
    }else if(name=="secukinumab"){
      if(sub[i,"weeks_delta_to_baseline"]==0){
        interval=c(1,7,14,21,28)
      }else{
        interval=28
      }
      if(diagnosis=="spa"){
        dose=150
      }else if(diagnosis=="psa"){
        dose=c(150,300)
      }
    }else if(name=="tocilizumab"){
      dose=162
      interval=c(7,14)
    }else if(name=="tofacitinib"){
      dose=c(5,10)
      interval=1
    }else if(name=="upadacitinib"){
      dose=15
      interval=1
    }else if(name=="ustekinumab"){
      if(diagnosis=="psa"){
        if(!(is.na(sub[i,"weight"])) && sub[i,"weight"]<100){
          dose=45
        }else if(!(is.na(sub[i,"weight"])) && sub[i,"weight"]>=100){
          dose=90
        }else{
          dose_issue=dose_issue+1
          interval_issue=interval_issue+1
          next
        }
        if(sub[i,"weeks_delta_to_baseline"]==0){
          interval=c(1,28)
        }else{
          interval=84
        }
      }else{
        dose_issue=dose_issue+1
        interval_issue=interval_issue+1
        next
      }
    }
    
    # check if drug is not part of the standard
    if(!(sub[i,"bio_drug_name"] %in% drug_names)){
      next
    }
    
    
    
    
    if(name=="infliximab"){
      if(!is.na(sub[i,"weight"])){
        data_dose=as.integer(sub[i,"bio_drug_dose"]/sub[i,"weight"])
      }
    }else{
      data_dose=sub[i,"bio_drug_dose"]
    }
    strike=0
    varians_strike=0
    for(j in 1:length(dose)){
      if(!(data_dose %in% dose[j])){
        strike=strike+1
      }
      if(!(data_dose %in% seq(dose[j]*0.9,dose[j]*1.1,0.1))){
        varians_strike=varians_strike+1
      }
      if(data_dose %in% dose[j] || data_dose %in% seq(dose[j]*0.9,dose[j]*1.1,0.1)){
        dose_pos=which(dose==sub[i,"bio_drug_dose"])
      }
      if(strike==length(dose)){
        dose_issue=dose_issue+1
      }
      if(varians_strike==length(dose)){
        dose_varians_issue=dose_varians_issue+1
      }
    }
    
    data_interval=sub[i,"bio_drug_dosing_interval"]
    strike=0
    varians_strike=0
    
    if(!(is.na(data_interval))){
      if(length(dose)==length(interval) && length(dose_pos)!=0){
          if(is.na(interval[dose_pos]) || !(data_interval %in% interval[dose_pos])){
            interval_issue=interval_issue+1
          }
          if(is.na(interval[dose_pos]) || !(data_interval %in% seq(interval[dose_pos]-7,interval[dose_pos]+7))){
            interval_varians_issue=interval_varians_issue+1
          }
      }else{
        for(j in 1:length(interval)){

          if(!(interval[j] %in% data_interval)){
            strike=strike+1
          }
          if(!(data_interval %in% seq(interval[j]-7,interval[j]+7))){
            varians_strike=varians_strike+1
          }
          if(strike==length(interval)){
            interval_issue=interval_issue+1
          }
          if(varians_strike==length(interval)){
            interval_varians_issue=interval_varians_issue+1
          }
        }
      }
    }  
  }  

  if(name %in% unique(d$bio_drug_name)){
    dose_match=length(sub$patient_id) - dose_issue
    interval_match=length(sub$patient_id) - interval_issue 
  
    dose_match_percent=dose_match/length(sub$patient_id)*100
    interval_match_percent=interval_match/length(sub$patient_id)*100

    dose_varians_match=length(sub$patient_id) - dose_varians_issue
    interval_varians_match=length(sub$patient_id) - interval_varians_issue
  
    dose_varians_percent = dose_varians_match/length(sub$patient_id)*100
    interval_varians_percent = interval_varians_match/length(sub$patient_id)*100

    final_dose_match=paste(dose_match," (",round(dose_match_percent,3),"%)")
    final_interval_match=paste(interval_match," (",round(interval_match_percent,3),"%)")
  
    final_dose_varians_match = paste(dose_varians_match," (",round(dose_varians_percent,3),"%)")
    final_interval_varins_match = paste(interval_varians_match," (",round(interval_varians_percent,3),"%)")
  
    dosematch <- append(dosematch,final_dose_match)
    intervalmatch <-append(intervalmatch,final_interval_match)
  
    dosevariansmatch <- append(dosevariansmatch,final_dose_varians_match)
    intervalvariansmatch <- append(intervalvariansmatch,final_interval_varins_match)
    
    final_names <- append(final_names,name)
    
  }
}


df<-data.frame(drugs=final_names,
               DoseMatch=dosematch,
               DoseVarians=dosevariansmatch,
               IntervalMatch=intervalmatch,
               IntervalVariansMatch=intervalvariansmatch)
colnames(df)<-c("bDMARDS",
                "dosis match <n(%)>",
                "dosis match +/-10% <n(%)>",
                "interval match <n(%)>",
                "interval match +/- 7 days <n(%)>")

formattable(df)


```





## 11. Further ideas for screening that may be considered at a later stage

 - Transform data to one row = one treatment series per patient, 'transformed data', note that this requires careful selection of baseline visit and follow-up visit using certain time periods and completeness considerations, calculated using bio_drug_start_date as "key" variable (required for next step). Pool data from all countries, 'pooled data'
 - mice::md.pattern applied to 'transformed data'
 - Compare 'pooled data' across countries by using various plots


